The imprint of global magma oceans on exoplanet demographics

### 2022-12-09 src/tex/ms.tex
transition to testing the runaway GH transition

Figure~\ref{fig:radiuscomparison} shows the different mass-radius relations of the three cases for a fiducial water mass fraction of $x_{H_2O}= \wrr$.
In general, steam atmospheres (case~B) cause a significant radius increase, which is slightly reduced when water incorporation in the melt is allowed (case~C).
Our nominal simulation setup is such that all planets receiving an instellation $S < S_\mathrm{thresh}$ follow relation~A, and all planets with $S > S_\mathrm{thresh}$ follow relation~C.

\begin{note}
\todo[inline]{Transition to tests of the trend:}
Figure~\ref{fig:has_magmaocean} shows that the subpopulation of planets with magma oceans is apparent in the synthetic dataset.
    In the following, we test if and under what conditions this effect is large enough to be detected with high significance.
\end{note}

>>>>

Figure~\ref{fig:radiuscomparison} shows the different mass-radius relations of the three cases for a fiducial water mass fraction of $x_{H_2O}= \wrr$.
In general, steam atmospheres (case~B) cause a significant radius increase, which is slightly reduced when water incorporation in the melt is allowed (case~C).
Our nominal simulation setup is such that all planets receiving an instellation $S < S_\mathrm{thresh}$ follow relation~A, and all planets with $S > S_\mathrm{thresh}$ follow relation~C.
This introduces a sharp discontinuity of average planet radii and bulk densities as a function of stellar irradiation.
In the following, we test if and under what conditions this trend is large enough to be detected with high significance.
